Testing Charts: viewer's perceptual accuracy in surveys

### 2023-06-16 SDSS-2023/testing-charts-accuracy.qmd
settings for figures and images

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = F, 
                      eval = F, 
                      fig.path="./images/", 
                      fig.env="figure*", 
                      fig.align = "center",
                      dpi = 72) 
library(readr)
library(tidyverse)
library(knitr)
library(bibtex)
theme_set(theme_bw())

@@

```{r eyefitting-lmer-residualplots, warning = F, message = F}
#| fig-cap: "quarto figure caption."
#| out-width: \columnwidth
#| label: fig-label-we-decide-on
#| fig-res: 300
#| fig-width: 9 # set only if different from the default
#| fig-height: 9
#| fig-env: figure
#|

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = F, 
                      eval = T, 
                      fig.path="./figures/", # figures are created on the fly, images are pictures like the stimuli
                      fig.env="figure*", 
                      fig.align = "center",
                      dpi = 72, # we can set the resolution up to 300 later.
                      cache = TRUE) 
library(readr)
library(tidyverse)
library(knitr)
library(bibtex)
theme_set(theme_bw())

@@

```{r showplot, warning = F, message = F}
#| fig-cap: "quarto figure caption."
#| out-width: \columnwidth
#| label: fig-label-we-decide-on
#| fig-res: 300
#| fig-width: 9 # set only if different from the default
#| fig-height: 9
#| fig-env: figure
#|
